|

### 2021-07-25 article/articleCustomerDropoutMembership.Rmd
upd

---
title: |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. The current template adapts part of the Rmd code by [Paul C. Bauer](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown), Mannheim Centre for European Social Research.]\vspace{0.5cm}
  |
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article.\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin = 1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
---

@@

     ##https://opensource.com/article/19/5/python-3-default-mac

     ##Sys.setenv(RETICULATE_PYTHON = "C:/Users//AppData/Local/Microsoft/WindowsApps/python3")

   ##install.packages("reticulate")
   library(reticulate)
   ##use_python("/Library/Frameworks/Python.framework/Versions/3.8/bin/python3")

   ##use_virtualenv("C:/Users/mangelo.EEG/Documents/python")

   ##knitr::opts_chunk$set(python.reticulate = FALSE)

   # library(devtools) # before this you may need to install devtools
   # install_github("hemken/Statamarkdown")

   }
```

```{r RETICULATE,echo = FALSE}
#Sys.setenv(RETICULATE_PYTHON = "C:/Program Files/Python39/python.exe")
#library(reticulate)
#use_virtualenv("C:/Users/mangelo.EEG/Documents/python")
```

@@

\renewcommand{\baselinestretch}{0.5}\normalsize
[//]: # \tableofcontents
\renewcommand{\baselinestretch}{1.1}\normalsize

@@

```{r Stats, echo = TRUE, message = FALSE}
library(dplyr)
library(dlookr)
library(ggplot2)

@@

The average age in our data is `r round(mean(airquality$Temp,na.rm = TRUE),1)`.

# Tables {#sec:tables}
R Markdown PDF is now able to produce good tables with our output. For `stargazer` the label is contained in the function, while for `kable` it's contained in the chunk name.

@@

Table \@ref(tab1) shows data's summary statistics.^[You can reference the table as \@ref(tab1cars).] `stargazer()` is and excellent solution to export outputs.

```{r Export Stats, echo = TRUE, message = FALSE, warning = FALSE, paged.print = FALSE, results = "asis"}
library(stargazer)
stargazer(cars,
          title = "Summary table with stargazer",
          label = "tab1cars",
          table.placement = "h",
          header = FALSE)
```

@@

## Graphs with R
You can insert figures like this. One would like to produce and insert them on the fly in the `.rmd` file. Figure \@ref(fig:fig-1) is such an example.

@@

## Example: ggplot2 graphs
See the `ggplot2` output reported in Figure \@ref(fig:fig-2).

@@

## Another example using Plotly
With `Plotly` we can produce interactive graphs which play well, for example, once can embedded 
in html webpages (drop by  [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/) 
for an example). One can insert this type of graphs in R Markdown PDF using `Orca` (it generates 
static images from Plotly graphs). 
Go [here](https://github.com/plotly/orca#installation) to check how to install it. 
See Figure \@ref(fig:fig-3) for an example.

@@

\begin{figure}[ht]
\centering
\caption{Example: export a Plotly figure using `orca`}\label{fig:fig-3}
	\includegraphics[width = 0.9\linewidth]{../figures/teste.png}
\begin{flushleft}
\end{flushleft}
\end{figure}
\vspace{-1.2cm}

```{r exemploMedia}
# Lets create a value for example

@@

```
The criminal rate is `r media`\%o.

@@

\begin{equation}
f\left(k\right) = \binom{n}{k}p^k\left(1-p\right)^{n-k} \label{eq:binom}
\end{equation}

See Equation \@ref(eq:binom).

\begin{align}
y_{ijt} = \beta x_{ijt} + \eta_i + \gamma_j + \lambda_t + \varepsilon_{ijt}
\end{align}

```{r echo = TRUE, message = FALSE, warning = FALSE, paged.print = FALSE, results = "asis"}
library(stargazer)
stargazer(cars,
          title = "Summary 24",
          label = "tab24",
          table.placement = "ht",
          header = FALSE)
```

@@

Check the replication package for Bonhomme, Lamadon and Manresa (2019): https://github.com/tlamadon/blm-replicate

@@

# References {-}

<div id = "refs"></div>

# Appendix: Chunk options {-}

>>>>

---
title: |
  |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. The current template adapts part of the Rmd code by [Paul C. Bauer](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown), Mannheim Centre for European Social Research.]\vspace{0.5cm}
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article. Here we can place more info.\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin = 1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{hyperref}
editor_options: 
  markdown: 
    wrap: 80
---

@@

##https://opensource.com/article/19/5/python-3-default-mac
#Sys.setenv(RETICULATE_PYTHON = "C:/Users//AppData/Local/Microsoft/WindowsApps/python3")

#install.packages("reticulate")
#library(reticulate)
#virtualenv_create("artigosurvival",python_version="3.7.10")
#use_virtualenv("artigosurvival", required = TRUE)
}   
```

```{r RETICULATE,echo = FALSE}
#set environment first
Sys.setenv(RETICULATE_PYTHON="C:\\Users\\sobre\\anaconda3\\envs\\survival\\python.exe")
#call reticulate
library(reticulate)
#activate environment
use_condaenv("survival", required = TRUE)
#use_virtualenv("C:/Users/mangelo.EEG/Documents/python")
```

@@

\renewcommand{\baselinestretch}{0.5}\normalsize

\renewcommand{\baselinestretch}{1.1}\normalsize

@@

```{r Stats1, echo = TRUE, message = FALSE}
library(dplyr)
library(dlookr)
library(ggplot2)

@@

# Experimental Results

## Data description

```{r get_data, echo = FALSE, message = FALSE, warning=FALSE}
library(stargazer)
library(readxl)
library(dplyr)
library(visdat)

df_members <- read_excel("../data/membershipData.xlsx")

names(df_members)
# rename column labels
names(df_members) <- c("num_socio", "dt_inscription", "year", "birth_date",
                       "age", "sex", "marital_status", "category",
                       "monthly_fee", "occupation", "zip_code",
                       "dt_last_invoice", "dt_last_payment", "total_amount",
                       "total_matches", "season_matches",
                       "days_since_last_payment", "months_since_last_payment",
                       "dropout", "years_membership", "stadium_access",
                       "quart_stadium_entries", "inscription_month")

names(df_members)

# select relevant variables
df_members <- df_members %>%
select(year, age, sex, marital_status, monthly_fee, total_amount, total_matches,
       season_matches, months_since_last_payment, dropout, years_membership,
       stadium_access, quart_stadium_entries,inscription_month)

str(df_members)
vis_dat(df_members) #check
```

Table \@ref(tab:tab1cars) shows data's summary statistics.[^1] `stargazer()` is
and excellent solution to export outputs.

[^1]: You can reference the table as \@ref(tab1cars).

```{r Export Stats0, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(stargazer)
df_summary <- summary(df_members, object)
stargazer(df_members,
          title = "Summary statistics",
          label = "tab1cars",
          table.placement = "h",
          header = FALSE,
          summary = TRUE,
          summary.stat = c("min", "p25", "median", "p75", "max", "median", "sd")
         )

Teste \@ref(tab:summarytable)

```{r summarytable, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(gtsummary)
library(kableExtra)

tbl <- df_members %>%
    tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})",
                                 all_categorical() ~ "{p}%")
               )
as_kable_extra(tbl,booktabs=T,caption="Summary statistics")
```

```{python Py,eval=TRUE,echo=TRUE}
from pysurvival.utils.display import correlation_matrix
import pandas as pd
import numpy as np

col = ['sex','marital_status','quart_stadium_entries']

df_members = r.df_members #copy r dataframe to python

df_members = pd.get_dummies(df_members, columns=col,drop_first=True)

# Creating the time and event columns
time_column = 'years_membership'
event_column = 'dropout'

# Extracting the features
features = np.setdiff1d(df_members.columns, [time_column, event_column] ).tolist()

correlation_matrix(df_members, figure_size=(10,10), text_fontsize=6)
```

The average age in our data is `r round(mean(df_members$age,na.rm = TRUE),1)`.

# Tables {#sec:tables}

R Markdown PDF is now able to produce good tables with our output. For
`stargazer` the label is contained in the function, while for `kable` it's
contained in the chunk name.

@@

@@

## Graphs with R

You can insert figures like this. One would like to produce and insert them on
the fly in the `.rmd` file. Figure \@ref(fig:fig-1) is such an example.

@@

## Example: ggplot2 graphs

See the `ggplot2` output reported in Figure \@ref(fig:fig-2).

@@

## Another example using Plotly

With `Plotly` we can produce interactive graphs which play well, for example,
once can embedded in html webpages (drop by
[here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/) for an
example). One can insert this type of graphs in R Markdown PDF using `Orca` (it
generates static images from Plotly graphs). Go
[here](https://github.com/plotly/orca#installation) to check how to install it.
See Figure \@ref(fig:fig-3) for an example.

@@

```{=tex}
\begin{figure}[ht]
\centering
\caption{Example: export a Plotly figure using `orca`}\label{fig:fig-3}
    \includegraphics[width = 0.9\linewidth]{../figures/teste.png}
\begin{flushleft}
\end{flushleft}
\end{figure}
\vspace{-1.2cm}
```
```{r exemploMedia}
# Lets create a value for example

@@

The criminal rate is `r media`%o.

@@

```{=tex}
\begin{equation}
f\left(k\right) = \binom{n}{k}p^k\left(1-p\right)^{n-k} \label{eq:binom}
\end{equation}
```
See Equation \@ref(eq:binom).

```{=tex}
\begin{align}
y_{ijt} = \beta x_{ijt} + \eta_i + \gamma_j + \lambda_t + \varepsilon_{ijt}
\end{align}
```
```{r echo = TRUE, message = FALSE, warning = FALSE, paged.print = FALSE, results = "asis"}
library(stargazer)
stargazer(cars,
          title = "Summary 24",
          label = "tab24",
          table.placement = "ht",
          header = FALSE)
```

@@

Check the replication package for Bonhomme, Lamadon and Manresa (2019):
<https://github.com/tlamadon/blm-replicate>

@@

# References {.unnumbered}

::: {#refs}
:::

# Appendix: Chunk options {.unnumbered}
